The \proglang{R} Package \pkg{forestinventory}: Design-Based Global and Small Area Estimations for Multiphase Forest Inventories

### 2018-09-11 revision/reviews.tex
update 11_09_2018(andi)

@@

@@

	\answerfin{Whereas we agree that they might be slightly more readable without the n2 fractions, the decision to include them was based on the fact that this is how the formulas were originally presented in Mandallaz's papers. We feel that the marginal loss in readability is offset by perfect continuity with the original notation.}
	% --------------------------- %

@@

	\answerfin{It has been added that the models require intercept terms.}
	% --------------------------- %

@@

The paper is rather long which can be a good or bad thing. I think that the 2 and 3 phase estimators are so similar that it may be sufficient to present, for example, SAE only for the 2 phase estimator and global estimation only for the 3 phase estimator. The same is true for the exhaustive and non-exhaustive estimators. Describing just once that in all cases both types are possible (as done for cluster sampling), would make the text a lot easier to read. \\
\\
\answerfin{Different versions of this article were written that attempted to shorten it in ways just like the review mentioned.  However, we ultimately decided that the purpose of this article is to bridge the gap between likely users of the software (e.g. forest engineers and technical practitioners) and the mathematical details that might be beyond their skillset.  For this reason, we decided to ensure that every function call was connected explicitly to the underlying formula that it applies and a citation is given for those interested in further technical details.  We believe this also enables the reader to write their own routines using the functions which can be used to error check our routines. Considering that the current length is not excessively long compared to other JSS papers, we strongly prefer to not to shorten sections merely for the sake of making the article shorter.} \\

Also section 5 on CIs could be considerably shortened. Needs to be a section on its own right? Sections 6 and 7 are very interesting but the R code under 7.1 could probably be condensed a lot.\\
\\
\answerfin{Reviewer 1 made a very valid criticism about designed-based confidence intervals when the sampling fraction is too small that we would like to include in the paper and Section 5 is the most logical place to put it.} \\

@@

\answerfin{When the package was orginally beta tested at the Swiss Federal Institute of Forest, Snow and Landscape Management on likely operational users as well as forest engineers, the most contentious area for confusion was the calculation of explanatory variables in the exhaustive case.  The reviewer appears to have confirmed that confusion in the previous paragraph, which is explained in the section on calculating explanatory variables.  It is explictly stated that the exact exhaustive mean vector can only be calculated for explanatory variables based on means (note that polygon layers are means of binary variables). It has now been explicitly added as an example that order statistics are not included in this category with the reviewers example given.  It is already explicitly stated that the size of the support should ideally be chosen to achieve a best possible explanatory power of the regression model on page 9 and a citation has been added for the interested reader.} \\

@@

\answerfin{The population doesn't need to be tessellated and can be allowed to overlap or not use all the wall-to-wall map in the infinite population approach. This is already mentioned on page 9.  Section 2.1 discusses the Infinite Population Approach.  Some brief discussion comparing to the finite is included, but as this package is about software written for the infinite not finite approach, we prefer not to delve too deeply into a topic that makes little practical difference.} \\

@@

\answerfin{This is true, but it is already stated many times that the synthetic estimators will usually have a smaller variance than estimators incorporating the regression model uncertainties, but at the cost of a potential bias making them seem deceptively optimistic (see pages 5, 13 (twice), 14, 16 (this is explained here using a concrete example), 21, 26 and 30)} \\

@@

\answerfin{Removing outliers is more of a common practice in model-dependent estimation, which is beyond the scope of this article.  You should never remove outliers in design-based estimation unless you can defend the belief that the resulting (and self-inflicted) non-response is missing at random.  The observed value of the the response/explanatory variable is fixed at each $x$ so deleting an observation effectively means the plot at x has been removed from the forest.  For temporal mismatches this is pretty much indefensible because the outliers likely represent harvesting after the aerial measurement.  We initially included a discussion comparing design-based with model-dependent estimation but we ultimately decided that the paper has more focus if we concentrate only on explaining how to use this software under the design-based infinite population approach.  In any case, many citations are currently included that already discuss these issues.} \\

@@

\answerfin{A mention of sample plot boundary adjustments is now included in Section 2.1 with a citation.} \\

@@

\answerfin{Multiphase is now used consistently to match package's spelling}
% --------------------------- %

@@

\answerfin{Good point.  Has been changed accordingly.}
% --------------------------- %

@@

\answerfin{That suggestion only can be done if the plots form a perfect tesselation.  Circular units, the most common in NFIs, can't do this.  The rest of the sentence actually says "with respect to the forest area".  This is true.  Points can fill any forested area even if it is a fractal whereas a counter example forest area can always be given for any plot shape you put forward.  Extending your tesselation beyond the forest edge is possible, but this increases the weights for boundary cases which likely increases the variance.   Many of the cited articles in the infinite population approach already discuss this but the focus for this article is not a comparison of the finite and infinite approaches, but a presentation of a software package written under the infinite approach.}
% --------------------------- %

@@

\answerfin{The g-weight is the name of a variance estimator for the point estimate in eq.2 as opposed to another possible variance estimator here named the external estimator.  The origin of the g-weight name is more obvious in the citation provided in the same paragraph.  The g-weight is analogous to a hat matrix and can be extracted from the more compact form that was included in the article.  It the spirit of not being too verbose we chose the compact form. }
% --------------------------- %

@@

\answerfin{In this context "a biased estimate" is an estimate that is produced from a biased estimator.  It would be a bit tedious to explain every time that an given estimate was produced from a biased estimator.}
% --------------------------- %

@@

\answerfin{The "survey" package is in the finite population approach (aka list sampling).  It is mentioned on page 2.}
% --------------------------- %

@@

\answerfin{It is elegant in the sense that the SAE estimator is unbiased merely by modifying the design matrix.  It is not necessary to refit every small area with an indicator, but it is  how the package implemented the estimator.}
% --------------------------- %

@@

\answerfin{It says that "the formulas look similar to the synthetic estimators", because they are exactly same.  They merely have a modified design matrix.}
% --------------------------- %

@@

\answerfin{Change has been implemented.}
% --------------------------- %

>>>>

	\answerfin{Has been added.}
	% --------------------------- %

@@

	\answerfin{Has been changed.}
	% --------------------------- %

@@

@@

@@

The paper is rather long which can be a good or bad thing. I think that the 2 and 3 phase estimators are so similar that it may be sufficient to present, for example, SAE only for the 2 phase estimator and global estimation only for the 3 phase estimator. The same is true for the exhaustive and non-exhaustive estimators. Describing just once that in all cases both types are possible (as done for cluster sampling), would make the text a lot easier to read. Also section 5 on CIs could be considerably shortened. Needs to be a section on its own right? Sections 6 and 7 are very interesting but the R code under 7.1 could probably be condensed a lot.\\

@@

@@

@@

@@

@@

@@

\note{\textit{Andi}: There is a slight inconsistency in our article here: Our package says 'multiphase', but here we used 'multi-phase'. However, should we then also change 'two-phase' to 'twophase'?}

@@

@@

@@

@@

@@

@@

@@

@@

### 2018-09-11 rnw/Acknowledgements.Rnw
update 11_09_2018(andi)

We want to express our gratitude to Prof. H. Heinimann (Chair of Land Use Engineering, ETH Zurich) for supporting this study and providing the possibility of working on the package. We also want to thank Daniel Mandallaz for his support in completing the range of the already published estimators in the frame of the three-phase small area estimators, as well as many helpful discussions and advice throughout the implementation of our package. Our thanks also go to Meinrad Abegg for proofreading the manuscript, and to the Amt f{\"u}r Wald und Naturgefahren of the Swiss canton of grisons for providing the example data.

>>>>

We want to express our gratitude to Prof. H. Heinimann (Chair of Land Use Engineering, ETH Zurich) for supporting this study and providing the possibility of working on the package. We also want to thank Daniel Mandallaz for his support in completing the range of the already published estimators in the frame of the three-phase small area estimators, as well as many helpful discussions and advice throughout the implementation of our package. Our thanks also go to Meinrad Abegg for proofreading the manuscript, and to the Amt f{\"u}r Wald und Naturgefahren of the Swiss canton of Grisons for providing the example data.

### 2018-09-11 rnw/Main structure and modules of the Package.Rnw
update 11_09_2018(andi)

Most forest inventories gather terrestrial information by sending field crews to randomly (or systematically) selected points in the forest area defined by coordinates. The crew then defines a sample plot by measuring individual trees located within one or multiple constructed inclusion circles around the sample point $x$, and aggregating their characteristics (e.g., timber volumes) to local plot densities (e.g., the timber density in m$^3$/ha). The estimators implemented in \pkg{forestinventory} use the so called infinite population approach in order to bridge this inventory process to the mathematics behind the estimators. This approach assumes that the spatial distribution of the local density, $Y(x)$, over the forest area is determined by a fixed piecewise constant function, as visualized in Fig. \ref{fig:inf_pop_apr}. The population total of the target variable (e.g., the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which is depicted in Fig. \ref{fig:inf_pop_apr} as the volume under the density surface. From this perspective, the practical challenge is that the form of this function is unknown. Theoretically, we could get the total timber volume by observing the function value, i.e., the local density $Y(x)$, at each possible point $x$ over the forest area and taking their sum. However, this is impossible because there is an infinite number of points in the forest area. Our strategy is thus to take a sample of points, $s_2$, from an infinite population of possible points and use their associated local densities $Y(x)$ to estimate the integral $Y=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$ with $\hat{Y}=\frac{1}{n_2}\sum_{x \in s_2}Y(x)$.  The total timber volume can then be obtained by multiplying $\hat{Y}$ by the surface area of the forest, $\lambda(F)$.  All estimators included in \pkg{forestinventory} rest upon this theoretical perspective. The key point in the infinite population approach is that a local density value $Y(x)$ is associated with the sample point $x$, which constitutes the sample unit, and not with the sample plot area. This has some theoretical advantages over the finite population approach, where the sample units are the actual plot areas usually assumed to be either circular or rectangular.  This is mainly due to the impossibility of a perfect tessellation over an amorphous forest area by any choice of plot shape. Hence, the population in the finite approach is, strictly speaking, not well defined with respect to the forest area. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

@@

\begin{figure}[htb]
\centering
\resizebox{1\hsize}{!}{\includegraphics{fig/Package_structure_5.eps}}
\caption{Structure of the multi-phase estimators in the \proglang{R} package \pkg{forestinventory}.}
\label{fig:struct_package}
\end{figure}

>>>>

Most forest inventories gather terrestrial information by sending field crews to randomly (or systematically) selected points in the forest area defined by coordinates. The crew then defines a sample plot by measuring individual trees located within one or multiple constructed inclusion circles around the sample point $x$, and aggregating their characteristics (e.g., timber volumes) to local plot densities (e.g., the timber density in m$^3$/ha). The estimators implemented in \pkg{forestinventory} use the so called infinite population approach in order to bridge this inventory process to the mathematics behind the estimators. This approach assumes that the spatial distribution of the local density, $Y(x)$, over the forest area is determined by a fixed piecewise constant function, as visualized in Fig. \ref{fig:inf_pop_apr}. The population total of the target variable (e.g., the total timber volume of the forest) is mathematically equivalent to the integral of that density function, which is depicted in Fig. \ref{fig:inf_pop_apr} as the volume under the density surface. From this perspective, the practical challenge is that the form of this function is unknown. Theoretically, we could get the total timber volume by observing the function value, i.e., the local density $Y(x)$, at each possible point $x$ over the forest area and taking their sum. However, this is impossible because there is an infinite number of points in the forest area. Our strategy is thus to take a sample of $n_2$ points, $s_2$, from an infinite population of possible points and use their associated local densities $Y(x)$ to estimate the integral $Y=\frac{1}{\lambda(F)}\int_{F}Y(x)dx$ with $\hat{Y}=\frac{1}{n_2}\sum_{x \in s_2}Y(x)$.  The total timber volume can then be obtained by multiplying $\hat{Y}$ by the surface area of the forest, $\lambda(F)$.  All estimators included in \pkg{forestinventory} rest upon this theoretical perspective. The key point in the infinite population approach is that a local density value $Y(x)$ is associated with the sample point $x$, which constitutes the sample unit, and not with the sample plot area. This has some theoretical advantages over the finite population approach, where the sample units are the actual plot areas usually assumed to be either circular or rectangular.  This is mainly due to the impossibility of a perfect tessellation over an amorphous forest area by any choice of plot shape. Hence, the population in the finite approach is, strictly speaking, not well defined with respect to the forest area. The consideration of an underlying infinite population of sample points will also play an important role when incorporating auxiliary information in the frame of two- and three-phase estimation methods.

@@

\begin{figure}[htb]
\centering
\resizebox{1\hsize}{!}{\includegraphics{fig/Package_structure_5.eps}}
\caption{Structure of the multi-phase estimators in the \proglang{R} package \pkg{forestinventory}. All estimators are also available for cluster sampling.}
\label{fig:struct_package}
\end{figure}
